Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-12-08 grove-paper.tex
Revise Section 2.4

However, there is one case where we need a more precise cursor.
That is when a vertex has a multi-child conflict (e.g. TODO in FIG:TODO).
We want users to beable to put their cussor on either the conflict as a whole
(e.g., TODO: \{ x | y \})
or on an individual element (e.g., x or y).
In the former case, a pair of a vertex and a child position suffices.
For the latter case, we represent cursors by an edge identifier (e.g., TODO in TODO:FIG).

@@

All in our system edits use edge and vertex identifiers, and user
cursors do not affect the interpretation of graph edits.
Thus, cursors are not part of the graph representation
and need not be communicated to other users.

However, in a collaborative setting, seeing the cursors of other users
and be useful.
Thus, the editor announce cursor position to other editors,
At any point in time, the announcement for a particular user with
the most recent timestamp is used.

>>>>

However, there is one case where we need a more precise cursor.
That is when a vertex has a multi-child conflict (e.g. TODO in FIG:TODO).
We want users to beable to put their cussor on either the conflict as a whole
(e.g., TODO: \texttt{\{ x | y \}})
or on an individual element (e.g., \texttt{x} or \texttt{y}).
In the former case, a pair of a vertex and a child position suffices.
For the latter case, we represent cursors by an edge identifier (e.g., TODO in TODO:FIG).

@@

In our system all edits use edge and vertex identifiers, and user
cursors do not affect the interpretation of graph edits.
Thus, cursors need not be communicated to other users.
However, in a collaborative setting, seeing the cursors of other users
can be useful.
For this purpose, editors can announce their cursor position to other editors.
At any point in time, the announcement
with the most recent timestamp
for a particular user
is used.
